\textsc{spiderman}: an open source code to model phase curves and secondary eclipses.

### 2016-10-18 ms.tex
stellar brightness

In order to recover any useful physical parameters of the planet, it is necessary to place constraints on the \emph{absolute} scale or brightness of the system.

@@

For the star however, we can do better than this. From high resolution spectroscopy and stellar modelling, there are often good constraints on the effective temperature and surface gravity of the star, and therefore the stellar type.

>>>>

In order to recover any useful physical parameters of the planet, it is necessary to place constraints on the \emph{absolute} scale or brightness of the system. Somewhat counter-intuitively, these constraints only need to be \emph{as a function of surface area}, i.e., on the specific intensity of the system components, not on their total luminosity.

To see that this is indeed the case, consider a case where the radii of both the planet and the star have both been underestimated by a factor of 2, such that the total luminosity will have been underestimated by a factor of 4. If the planetary and stellar specific flux distributions remains the same, The secondary eclipse depth and phase curve amplitude both scale as $(R_p / R_*)^2$, so are unchanged.

$(R_p / R_*)^2$ is of course constrained well by the primary transit.

@@

For the star however, we can do better than this. From high resolution spectroscopy and stellar modelling, there are often good constraints on the effective temperature and surface gravity of the star
